HO unification from object language to meta language

### 2024-03-23 paper/appendix.tex
url
use map

@@

  type tm->fm map -> ho.tm -> fo.fm -> o.
  tm->fm _ (ho.con C)  (fo.fcon C).
  tm->fm L (ho.lam B1) (fo.flam B2) :- 
    pi x y\ tm->fm _ x y => tm->fm L (B1 x) (B2 y).
  tm->fm L (ho.app L1) T :- forall2 (tm->fm L) L1 [Hd|Tl], 
    fo.mk-app Hd Tl T.
  tm->fm L (ho.uva VM TL) T :- mem L (mapping (fv VO) (hv VM _)), 
    forall2 (tm->fm L) TL T1, fo.mk-app (fo.fuva VO) T1 T.

>>>>

This appendix contains the entire code described in this paper.
The code can also be accessed at the URL: \url{https://github.com/FissoreD/paper-ho}

@@

  type tm->fm map -> ho.tm -> fo.fm -> o.
  tm->fm _ (ho.con C)  (fo.fcon C).
  tm->fm L (ho.lam B1) (fo.flam B2) :- 
    pi x y\ tm->fm _ x y => tm->fm L (B1 x) (B2 y).
  tm->fm L (ho.app L1) T :- map (tm->fm L) L1 [Hd|Tl], 
    fo.mk-app Hd Tl T.
  tm->fm L (ho.uva VM TL) T :- mem L (mapping (fv VO) (hv VM _)), 
    map (tm->fm L) TL T1, fo.mk-app (fo.fuva VO) T1 T.

### 2024-03-23 paper/main.tex
use map

\noindent
TODO: about the cut\marginpar{should we rename forall2 into map}

@@

In this paper we assume to have an implementation of \Ue that satisfies
properties \ref{prop:correct-ml,prop:complete-ml}. Although we provide an
implementation in the appendix (that we used for testing purposes) we only
describe its signature. Elpi is expected to provide this brick, as well as
any other implementation of $\lambda$Prolog.

>>>>

\noindent
TODO: about the cut

@@

In this paper we assume to have an implementation of \Ue that satisfies
properties~\ref{prop:correct-ml} and~\ref{prop:complete-ml}. Although we provide an
implementation in the appendix (that we used for testing purposes) we only
describe its signature here. Elpi is expected to provide this brick, as well as
any other implementation of $\lambda$Prolog.
